Algebra Homework

### 2018-06-30 Algebra/Homework/Homework.tex
algebrah complet

\documentclass{article}

\input{../../definitions.tex}
\input{../algebra.tex}

@@

This may be displayed pictorially as follows:

@@

\def\secondcircle{(210:0.95cm) circle (1.5cm)}
\def\thirdcircle{(330:0.95cm) circle (1.5cm)}
\begin{tikzpicture}
	\begin{scope}
		\clip \secondcircle;
		\fill[cyan] \thirdcircle;
	\end{scope}
	\draw \secondcircle node [text=black,below left] {$A$};
	\draw \thirdcircle node [text=black,below right] {$B$};
\end{tikzpicture}

@@

We know our function $\psi$ is not a monomorphism as $\card G > \card{A(S)}$. This means that $\ker(\psi) \not= (e)$. Now the last thing we need to show is $\ker(\psi) \subset H$. We can show this by considering $x \in G \setminus H$ and we find that in order for $x\in \ker(\psi)$ we would expect $\psi(x)\psi(y) = \psi(y)$ for all $y\in G$ which therefore means $T_yT_x(Ha) = T_y(Ha)$ for all $a \in G$. Consider $a = e$ and we get $Hexe = Hee$ so $Hx = H$ and this would mean $x \in H$ contradicting our previous statement. So as we know $\ker(\psi) \subset H$ and $\ker(\psi) \not= (e)$ and we already know that the kernel of a homomorphism is a normal subgroup, so as it is contained in $H$ which is of order 9, then this subgroup must be of order 3 or 9. This concludes our proof that either $H\normsubgroup G$ or there is $N \subset H$ with $\card N = 3$ such that $N \normsubgroup G$.

\subsection{Section 6}
\subsubsection{Question 11}
Suppose $G$ is a group and let $Z(G) = Z$. It is trivial to show that $Z \normsubgroup G$ so suppose further that $G/Z$ is cyclic. As $G/Z$ is cyclic it has some primitive element, $\eqclass g$. Now for any $x,y \in G$ we have $x \in Zg^n$ and $y \in Zg^m$ for some $n,m\in\mathbb N$ as all elements are in some coset of $Z$. We also have then that for some $z,w \in Z$ there is $x = zg^n$ and $y = wg^m$. We now do some manipulation
\begin{align*}
xy &= zg^nwg^m \\
&= zwg^ng^m \\
&= wzg^mg^n \\
&= wg^mzg^n \\
&= yz
\end{align*}
and we find $G$ is abelian. This means $Z = Z(G) = G$ so $G/Z = (e)$.

@@

\subsection{Section 7}
\subsubsection{Question 4}
We know that the kernel of a homomorphism is a normal subgroup, so let us construct $\varphi:G\to G_2$ as $\varphi(a,b) = b$. $\varphi$ is a homomorphism as $\varphi(a,b)\varphi(c,d) = ac = \varphi(ac,bd)$. Now we will show $\ker(\varphi) = \setbuilder{\pair{e_1}x}{x \in G_2}$.

\subsubsection{Question 5}
\subsubsection{Question 7}

\subsection{Section 8}
\subsubsection{Question 4}
\subsubsection{Question 6}
\subsubsection{Question 7}
\subsubsection{Question 8}
\subsubsection{Question 11}
\subsubsection{Question 12}

\subsection{Section 9}
\subsubsection{Question 1}
\subsubsection{Question 2}
\subsubsection{Question 3}

>>>>

\documentclass{article}
\input{../../definitions.tex}
\input{../algebra.tex}

@@

The pictures I will hand into you separately.

%This may be displayed pictorially as follows:

@@

%\def\secondcircle{(210:0.95cm) circle (1.5cm)}
%\def\thirdcircle{(330:0.95cm) circle (1.5cm)}
%\begin{tikzpicture}
%	\begin{scope}
%		\clip \secondcircle;
%		\fill[cyan] \thirdcircle;
%	\end{scope}
%	\draw \secondcircle node [text=black,below left] {$A$};
%	\draw \thirdcircle node [text=black,below right] {$B$};
%\end{tikzpicture}

@@

We know our function $\psi$ is not a monomorphism as $\card G > \card{A(S)}$. This means that $\ker(\psi) \not= (e)$. Now the last thing we need to show is $\ker(\psi) \subset H$. We can show this by considering $x \in G \setminus H$ and we find that in order for $x\in \ker(\psi)$ we would expect $\psi(x)\psi(y) = \psi(y)$ for all $y\in G$ which therefore means $T_yT_x(Ha) = T_y(Ha)$ for all $a \in G$. Consider $a = e$ and we get $Hexe = Hee$ so $Hx = H$ and this would mean $x \in H$ contradicting our previous statement. So as we know $\ker(\psi) \subset H$ and $\ker(\psi) \not= (e)$ and we already know that the kernel of a homomorphism is a normal subgroup, so as it is contained in $H$ which is of order 9, then this subgroup must be of order 3 or 9. This concludes our proof that either $H\normsubgroup G$ or there is $N \subset H$ with $\card N = 3$ such that $N \normsubgroup G$.
%
\subsection{Section 6}
\subsubsection{Question 11}
Suppose $G$ is a group and let $Z(G) = Z$. It is trivial to show that $Z \normsubgroup G$ so suppose further that $G/Z$ is cyclic. As $G/Z$ is cyclic it has some primitive element, $\eqclass g$. Now for any $x,y \in G$ we have $x \in Zg^n$ and $y \in Zg^m$ for some $n,m\in\mathbb N$ as all elements are in some coset of $Z$. We also have then that for some $z,w \in Z$ there is $x = zg^n$ and $y = wg^m$. We now do some manipulation
\begin{align*}
xy &= zg^nwg^m \\
&= zwg^ng^m \\
&= wzg^mg^n \\
&= wg^mzg^n \\
&= yz
\end{align*}
and we find $G$ is abelian. This means $Z = Z(G) = G$ so $G/Z = (e)$.

@@

\subsection{Section 7}
\subsubsection{Question 4}
\question{(a)}
We know that the kernel of a homomorphism is a normal subgroup, so let us construct $\pi_2:G\to G_2$ as $\pi_2(a,b) = b$. $\pi_2$ is a homomorphism as $\pi_2(a,b)\pi_2(c,d) = ac = \pi_2(ac,bd)$.

Now we will show $\ker(\pi_2) = N$. First let $\pair x{e_2} \in N$ and $\pair ab \in G$ and therefore $\pi_2(a,b)\pi_2(x,e_2) = be_2 = b = \pi_2(a,b)$ so $N \subset \ker(\pi_2)$. Now let $\pair xy\in\ker(\pi_2)$ and we get $\pi_2(x,y)\pi_2(a,b) = \pi_2(a,b)$ for $\pair ab \in G$. It follows then that $yb = b$ and therefore $y=e_2$ so $\ker(\pi_2) = N$.

\question{(b)}
Let $\pi_1:N\to G_1$ be defined as $\pi_1(a,{e_2}) = a$. We find that $\pi_1(a,e_2)\pi_1(b,e_2) = ab = \pi_1(ab,e_2)$ so it a homomorphism. If $\pi_1(a,e_2) = \pi_1(b,e_2)$ then $a =b$ so $\pi_1$ is a monomorphism. If $a \in G_1$ then $\pi_1(a, e_2) = a$ so $\pi_1$ is a isomorphism and thus $N \simeq G_1$.

\question{(c)}
Now let us define $\psi:G/N \to G_2$ as $\psi(N\pair ab) = b$. First we must show that this is a well defined function. Consider $N\pair ab = N\pair cd$, then it follows that $\pair ab = \pair n{e_2}\pair cd$. We get from this $b = e_2d = d$ so $\psi(N\pair ab) = b = d = \psi(N\pair cd)$. Before we show  We get for any $\pair ab, \pair cd \in G$,  $\psi(N\pair ab)\psi(N\pair cd) = bd = \psi(N\pair ab\pair cd)$ and therefore $\psi$ is a homomorphism. If $\psi(N\pair ab) = \psi(N\pair cd)$ then we get $b = d$. Now if $\pair xy \in N\pair ab$ then $x = na$ and $y = b$ for some $n \in G_1$, and thus $\pair xy \in N\pair cd$ as $x = na = nac^{-1}c$ and $b = d = ed$. This shows that $N\pair ab \subset N\pair cd$ and we get $N\pair cd \subset N\pair ab$ by symmetry so we conclude that if $\psi(N\pair ab)=\psi(N \pair cd)$ then $N\pair ab = N\pair cd$ so $\psi$ is a monomorphism. For any $g \in G_2$ I may construct $\pair ag$ with $a \in G_1$ and find that $\psi(N\pair ag) = g$ so $\psi$ is a isomorphism and thus $G_2 \simeq G/N$.

%Now consider the set $N\pair abN$, where $\pair ab \in G$. We find that for any $\pair nm \in N \pair ab N$, $n = n_1an_2$ and $m=e_2be_2 = b$ therefore as $\pair {n_1an_2}{b} \in N\pair ab$ due to $\pair{n_1an_2a^{-1}}{e_2} \in N$ we have $N\pair ab N \subset N\pair ab$. $N\pair ab \subset N\pair abN$ is trivial as $e\in N$ so $N\pair abe = N\pair ab \subset N\pair ab N$ and thus we get $N\pair abN = N\pair ab$ for any $\pair ab \in G$.

\question{(a)} We know that $H\inter N$ is a subgroup of $H$ as intersections form subgroups. Now consider $x \in H\inter N$ and $h \in H$. We wish to show that $h^{-1}xh \in H\inter N$. We know that $h^{-1}xh \in N$ as $N \normsubgroup G$, and as $h\in H$ and $n \in H$ we get $h^{-1}xh \in H$ so $h^{-1}xh \in H \inter N$ and thus $N\inter H \normsubgroup H$.

\question{(b)} For $x,y \in HN$ we get $x=h_1n_1$ and $y = h_2n_2$ for some $h_1,h_2 \in H$ and $n_1,n_2 \in N$, so $xy = h_1n_1h_2n_2$. Now $N\normsubgroup G$ so for some $\bar n \in N$ we get $h_1h_2\bar n{h_2}^{-1}h_2n_2 = h_1h_2\bar nn_2 \in HN$. For $hn \in HN$ we also have $(hn)^{-1} = n^{-1}h^{-1} = h^{-1}\bar nhh^{-1} = h^{-1}\bar n$ for some $\bar n \in N$. Therefore $HN$ is a subgroup of $G$.

\question{(c)} For all $n \in N$, we have $n = en \in HN$ as $e \in H$, therefore $N \subset HN$. Now as $N\normsubgroup G$ and $HN$ is a subgroup of $G$ then $N\normsubgroup HN$ is implied by $N\normsubgroup G$.

\question{(d)} Let us define $Q = H\inter N$. We find $H/Q = \setbuilder{hQ}{h\in H}$ and $HN/N = \setbuilder{hnN}{h \in H\land n \in N} = \setbuilder{hN}{h \in H}$. Now we define $\phi:HN/N \to H/Q$ as $\phi(hN) = hQ$. First to show that $\phi$ is a function let $qN = hN$ with $h,q \in H$. Now choose $qn \in \phi(qN) = qQ$. As $n \in Q$ this implies $n \in N$. As $qn \in qN = hN$ there is some $m \in N$ such that $hm = qn$. We then have $m = h^{-1}qn$ and as all $h,q,n \in H$ we get $m \in H$, and therefore $m \in Q$. It follows then that $qn = hm \in hQ$ and therefore $\phi(qN) = qQ \subset hQ = \phi(hN)$. By symmetry we may make the same argument that $\phi(qN)\supset \phi(hN)$ and therefore $\phi$ is well defined.

If we take $hN, qN \in HN/N$ we find $\phi(hN)\phi(qN) = (hQ)(qQ) = hqQ = \phi(hqQ)$. If $\phi(hN) = \phi(qN)$ then we find $hQ = qQ$. Now take $hn \in hN$ and as $hQ = qQ$ then there is some $v \in Q$ so that $he = h = qv$ and therefore $hn = qvn = q(vn) \in qN$. By symmetry we also know that for any $qn \in qN$, $qn \in hN$ so $hN = qN$. Finally for any $hQ \in H/Q$ we know $hN \in HN/N$ so that $\phi(hN) = hQ$ and therefore $\phi$ is a isomorphism giving $HN/N \simeq H/Q$.

\subsubsection{Question 7}
Let $\varphi: G\to G'$ be a homomorphism and onto and let $N \normsubgroup G$. Choose $a' \in G'$, and $n' \in \varphi(N)$. It follows that for some $a\in G$ and some $n \in N$, $\varphi(a) = a'$ and $\varphi(n) = n'$. Now if $a'^{-1}n'a' \in \varphi(N)$ then $\varphi(N) \normsubgroup G$.
\begin{align*}
a'^{-1}n'a' &= \varphi(a)^{-1}\varphi(n)\varphi(a) \\
&= \varphi(a^{-1})\varphi(n)\varphi(a) \\
&= \varphi(a^{-1}na)
\end{align*}
We know $a^{-1}na \in N$ and therefore $a'^{-1}n'a' \in \varphi(N)$ so $\varphi(N)\normsubgroup G'$.

\subsection{Section 8}
\subsubsection{Question 4}
Let $a$ and $b$ be elements with order 7 and 3 respectively. It follows that $b^{-1}ab = a^i$ for some $0 \le i < 7$. We then have 
\begin{align*}
a &= eae\\
& = b^{-3}ab^3\\
& = b^{-2}a^ib^2\\
&= b^{-1}a^{i^2}b \\
&= a^{i^3}
\end{align*}
and therefore $i^3 \equiv 1 \mod 7$. If we let $i = 2$ we find that $2^3=8\equiv1\mod7$ and additionally this is consistent with Fermat's little theorem so $2^6 \equiv 1^2 \equiv 1 \mod 7$. We go ahead then and define $b^{-1}ab = a^2$ so $ab=ba^2$. Now consider
\begin{align*}
a^nb^m &= a^{n-1}ba^2b^{m-1} \\
&= a^{n-k}ba^{2k}b^{m-1} \\
&= ba^{2k}b^{m-1} \\
&= b^2a^{4n}b^{m-2} \\
&= b^\ell a^{2^\ell n}b^{m-\ell} \\
&= b^ma^{2^mn}
\end{align*}
Now we can show that $G= \setbuilder{a^nb^m}{n\in\mathbb Z\land m\in\mathbb Z}$ is closed under this operation.
\begin{align*}
a^nb^ma^ob^p &= b^ma^{2^mn+o}b^p \\
&= b^{m+p}a^{2^p\left(2^mn+o\right)} \in G
\end{align*}
This is a group as it obviously has an identity $a^0b^0$ and gets inverses from it's closure with $(a^nb^m)^{-1} =b^{-m}a^{-n}= a^0b^{-m}a^{-n}b^0 \in G$. Finally it's order is 21 as we may make the bijection $f(a^nb^m) = (n\mod 7,m\mod 3) \in \mathbb Z/7\cross \mathbb Z/3$. This is well defined due to the assumed order of $a$ and $b$ in $G$. It is 1-1 as if $f(a^nb^m)=f(a^ob^p)$ then $n\equiv o\mod 7$ and $m\equiv p \mod 7$ so it follows that $a^nb^m = a^ob^p$. Finally $f$ is onto as for any $(n,m) = f(a^nb^m)$.

\subsubsection{Question 6}
Consider $\card{AB}$. From a previous problem we showed that $\card{AB}=\frac{\card{A}\card{B}}{\card{A\inter B}}$. $AB \subset G$ so $\card{AB}\le\card G$. From this it follows that $\card{A\inter B}= \frac{\card A\card B}{\card{AB}} \ge \frac{\card A\card B}{\card G} > \frac{\card{\sqrt G}\card{\sqrt G}}{\card G} = 1$, so $A\inter B$ must have more than just the identity.

\subsubsection{Question 7}
We know that $A\inter B$ is a subgroup of both $A$ and $B$ so $\card{A\inter B}|A$ and $\card{A\inter B} | B$ by Lagrange's theorem, which in turn implies that $\card{A\inter B} = 1$ as $\card A$ relatively prime to $\card B$ and therefore $A\inter B = (e)$. We also know that $\card{AB} = \frac{\card A\card B}{\card{A\inter B}} = \card A\card B$.

99 has prime divisors $3$ and $11$ so there is some element $a \in G$ with $o(a) = 3$ and $b\in G$ with $o(b) = 11$. It follows then that $o(ab) = 33$ so $(ab)$ is a subgroup of $G$ with order 33.

Now we construct as $S=\setbuilder{(ab)x}{x\in G}$ and $T_x:S\to S$ as $T_x((ab)y) = (ab)yx$, which we note is in $A(S)$. Now we construct $\psi:G\to A(S)$ as $\psi(x) = T_x$. We get that $\psi$ is homomorphism from our work chapter 2, section 4, and additionally that $\abs S = \frac{\card G}{\card{(ab)}} = 3$. Now $\psi$ is not a monomorphism as it's domain is larger then it's co-domain. We then conclude that $\ker(\psi)$ must be a non-trivial subgroup of $G$ as $\ker(\psi) \not = (e)$ and kernels are always normal subgroups.

If $G$ is of order 21 then let $a,b \in G$ such that $o(a) = 7$ and $o(b) = 3$ we then know that $b^{-1}ab = a^{i}$ for some $i$ and from this we get $i^3 \equiv 1 \mod 7$. Well for $i^3 \equiv 1\mod 7$ we need either $i =1$, $i= 2$, or $i = 4$. If $i = 1$ then we get $b^{-1}ab = a$ so $ab = ba$ and $G$ is abelian. So either $i = 2$ or $i = 4$. Now consider $c = b^2$, $o(c) = 3$ as we get $(c) = \set{b^2,b^4=b^1,b^3 = e}$. In question 4 we found that $a^nb^m=b^ma^{2^m+n}$ and here we find it more generally is $a^nb^m=b^ma^{i^mn}$. If $i = 2$ and we get
\begin{align*}
a^nc^m &= a^nb^{2m} \\
&= b^{2m}a^{2^{2m}n} \\
&= b^{2m}a^{\left(2^2\right)^mn}\\
&= c^ma^{4^mn}
\end{align*}
and therefore we find that even if we set $i = 2$ then we also have the group that we would get if $i=4$. This means the two must be isomorphic with the isomorphism $f(a^nb^m) = a^n\left(b^2\right)^m$.

\subsection{Section 9}
\subsubsection{Question 1}
Let $f:G_1\cross G_2 \to G_2\cross G_1$ be defined as $f(\pair{a}{b}) = \pair ba$. We have 
\begin{align*}
f(\pair ab)f(\pair cd) &= \pair ba\pair dc\\
& = \pair {bd}{ac} \\
&= f(\pair{ac}{bd}) \\
&= f(\pair ab\pair cd)
\end{align*}
so $f$ is a homomorphism. We have if $f(\pair ab) = f(\pair cd)$ then $\pair ba = \pair dc$ so $a = c$ and $b = d$, therefore $\pair ab=\pair cd$, so $f$ is a monomorphism. For any $\pair ab\in G_2\cross G_1$ we have $f(\pair ba) = \pair ab$ and $\pair ba \in G_1\cross G_2$ by definition so we have $f$ is an isomorphism. Therefore $G_1\simeq G_2$.

\subsubsection{Question 2}
Suppose $G_1$ and $G_2$ are cyclic groups of order $m,n$ respectively. The group $G_1\cross G_2$ has order $mn$ and therefore to say that $G_1\cross G_2$ is cyclic is equivalent to saying there is some element $\pair ab \in G_1\cross G_2$ with order $mn$. Now for any $\pair ab\in G_1\cross G_2$ we get $\pair ab^{mn} = \pair{a^{mn}}{b^{mn}} = \pair ee = e$, so therefore in order of $G_1\cross G_2$ not to be cyclic we need to show that for all elements there is some $i < mn$ such that $\pair ab = e$. Well this $i$ needs to be such that $n|i$ so that $b^i = e$ and $m|i$ so that $a^i = e$, and $i | ab$ by Lagrange's theorem. This exists if and only if $(m,n) \not = 1$ otherwise stated if and only if $m$ and $n$ are not relatively prime.

\subsubsection{Question 3}

\question{(a)}
Consider $f:G\to T$ as $f(a) = \pair aa$. We get $f(a)f(b) = \pair aa\pair bb = \pair{ab}{ab} = f(ab)$. If $f(a) = f(b)$ we get $\pair aa = \pair bb $and therefore $a=b$. Finally if $\pair aa \in T$ then $f(a) = \pair aa$ so we know $f$ to be an isomorphism.

\question{(b)} First iff $G$ is abelian is $G\cross G$ abelian.
\begin{proof}
	Let $G$ be abelian. It follows then that $\pair ab\pair cd = \pair{ac}{bd} = \pair{ca}{db} = \pair cd\pair ab$ so $G\cross G$ so $G$ is abelian implies $G\cross G$ is abelian. Let $G\cross G$ be abelian. Then as $G$ is isomorphic to the subgroup $\setbuilder{\pair gg}{g \in G}$ we get $G$ being abelian.
\end{proof}

So it follows that if $G$ is abelian then any subgroup is normal including $T$. If $T$ is a normal subgroup then we get for any $a,b,c \in G$ there exists $d\in G$ such that $\pair ab^{-1}\pair cc\pair ab = \pair dd$. This means  From this we get $a^{-1}ca = d = b^{-1}cb$, and further for any $g\in G$, $g^{-1}cg = d$. It logically follows then that $e^{-1}ce = d = c$. Now finally we have $a^{-1}ca = c$ for any $a,c\in G$ and by multiplying $a$ in the front we get $ca = ac$ for any $a,c\in G$ so $G$ is abelian.

%and from that if we choose any $g \in G$ we still have $\pair ag^{-1}\pair cc\pair ag = \pair ff$, however from this we get $a^{-1}ca = f$ so $f= d$ and therefore $a^{-1}ca =d =f = g^{-1}cg$

\subsection{Section 11}
\subsubsection{Question 3}
Let $ c\in C\left(x^{-1}ax\right)$. By definition we get $cx^{-1}ax=x^{-1}axc$. It follows from this that $x^{-1}ax = c^{-1}x^{-1}axc =(xc)^{-1}axc$, and therefore $xcx^{-1} \in C(a)$. This means $x^{-1}xcx^{-1}x  = c \in x^{-1}C(a)x$ so $C\left(x^{-1}ax\right) \subset x^{-1}C(a)x$. Going the other direction, let $x^{-1}cx \in x^{-1}C(a)x$, so $ca = ac$. We then get $\left(x^{-1}cx\right)\left(x^{-1}ax\right) = x^{-1}cax = x^{-1}acx = \left(x^{-1}ax\right)\left(x^{-1}cx\right)$. This means $x^{-1}cx \in C(x^{-1}ax)$ and we conclude our proof that $C\left(x^{-1}ax\right) = x^{-1}C(a)x$.

\subsubsection{Question 4}
Let $\varphi(b) \in \varphi(C(a))$ therefore $b \in C(a)$. Now we get $\varphi(a)\varphi(b) = \varphi(ab) = \varphi(ba) = \varphi(b)\varphi(a)$ so $\varphi(b) \in C(\varphi(a))$, and therefore $\varphi(C(a)) \subset C(\varphi(a))$.

Let $b \in C(\varphi(a))$, and as $\varphi$ is 1-1 there is some $c$, such that $\varphi(c) = b$. Now we have $ac = \varphi^{-1}(\varphi(ac))$, which we can do again due to $\varphi$ being 1-1 and onto. This gives 
\begin{align*}
ac &= \varphi^{-1}(\varphi(ac))\\
& = \varphi^{-1}(\varphi(a)\varphi(c))\\
& = \varphi^{-1}(\varphi(c)\varphi(a))\\
&= \varphi^{-1}(\varphi(ca)) \\
&= ca
\end{align*}
so $c \in C(a)$ and thus $\varphi(c) = b \in \varphi(C(a))$ so we finish with $\varphi(C(a)) = C(\varphi(a))$.

For any subgroup $H$ of $G$ we have $H \subset N(H)$ as if we choose $h \in H$ we get $h^{-1}gh \in H$ if $g \in H$ due to closure and we get $g \in H$ if $h^{-1}gh \in H$ as we would have $g = hqh^{-1}$ for some $q\in H$. This simply shows that if $P$ is a $p$-Sylow subgroup of $G$ then it must also be a subgroup of $N(P)$ and as $N(P)$ is trivially a subgroup of $G$, by Lagrange's theorem we know if there was some $p$-Sylow subgroup of $N(P)$ larger then $H$ it would be a subgroup of $G$ and thus $P$ would no longer be a $p$-Sylow group, so therefore $P$ is a $p$-Sylow subgroup of $H$.

let $Q$ be a subgroup of $N(P)$ such that $\card Q = \card P = p^n$ Now consider the set $PQ = \setbuilder{pq}{p \in P\land q\in Q}$, we wish to show this is a group. Consider $p_1q_1p_2q_2$ with $p_1,p_2 \in P$ and $q_1,q_2\in Q$. Now $p_1q_1p_2q_2 = p_1\left(q_1p_2{q_1}^{-1}\right)q_1q_2 = p_1p_3q_1q_2$ with $p_3 = q_1p_2{q_1}^{-1}$ and we know $p_3 \in P$ as $ Q \subset N(P)$. This shows closure of $PQ$. Now we get inverses as $(pq)^{-1} = q^{-1}p^{-1} = eq^{-1}p^{-1}e$ and $eq^{-1} \in PQ$ as is $p^{-1}e\in PQ$, considering that we already have $PQ$ is closed we have now shown $PQ$ to be a subgroup of $G$ and as both $P$ and $Q$ are subgroups of $N(P)$ this is also a subgroup of $N(P)$. Finally we consider the size of this group, $\card{PQ} = \frac{\card{P}\card{Q}}{\card{P\inter Q}}$. $\card{P\inter Q} = p^k$ for some $k \le n$ as it is a subgroup of both $P$ and $Q$ which have order $p^n$. $\card P\card Q = p^{2n}$, so $\card{PQ} = p^{2n-k}$. It follows that $k = n$ as otherwise $P$ would not be $p$-Sylow group. Therefore $\card{P\inter N}= 2^p$ so $P\inter N = P$. Finally we then conclude that $N = P$ and therefore $P$ is the only $p$-Sylow subgroup of $N(P)$.

\subsubsection{Question 14}
Suppose $a \sim b$ if $a^{-1}Pa = b^{-1}Pb$. We get that $\sim$ is an equivalence relation very quickly as
\begin{itemize}
	\item $a\sim a$ trivial
	\item $a \sim b \implies a^{-1}Pa=b^{-1}Pb\implies b^{-1}Pb=a^{-1}Pa \implies b\sim a$.
	\item if $a\sim b$ and $b\sim c$ then $a^{-1}Pa =b^{-1}Pb = c^{-1}Pc$ so $a\sim c$.
\end{itemize}

Now we may construct equivalence classes $\eqclass{a} = \setbuilder{x\in G}{x \sim a}$, and notice that the question of how many distinct $a^{-1}Pa$ there are is the same as how many equivalence classes there are. Now first consider $\eqclass e$. This is the set of all $x$ such that $x^{-1}Px = e^{-1}Pe = P$. This trivially contains all of $P$ and is in-fact itself a subgroup of $G$ as
\begin{itemize}
	\item If $a, b \in \eqclass e$ then $a^{-1}Pa = b^{-1}Pb = P$. It follows that $\left({ab}\right)^{-1}Pab = b^{-1}a^{-1}Pab = b^{-1}Pb = P$ and therefore $ab \in \eqclass e$.
	\item If $a \in \eqclass e$ then $a^{-1}Pa = P$. It follows then that $aPa^{-1} = aa^{-1}Paa^{-1} = P$ so $a^{-1} \in \eqclass e$.
\end{itemize}
so this means it's order is a multiple of $\card P = p^n$. Finally we now wish to prove that for all $a,b \in G$, $\card{\eqclass{a}}=\card{\eqclass{b}}$. To do this we construct a bijection $f_a:\eqclass e\to\eqclass a$ as $f_a(x) = xa$.

First to show this function is well defined. If $x\in \eqclass e$ then $x^{-1}Px = P$ and therefore $(xa)^{-1}Pxa = a^{-1}x^{-1}Pxa = a^{-1}Pa$ so $f_a(x)\in\eqclass a$ and our function is shown to be well defined. Next it is 1-1 as if $f_a(x) = f_a(y)$ then $ax = ay$ and $x=y$. Our function is also onto as if I choose $y\in \eqclass a$ then consider $x=ya^{-1}$, if $x\in \eqclass e$ then we get $f_a(x) = y$ and $f_a$ would be onto. To show $x\in\eqclass e$ we consider $x^{-1}Px=\left(ya^{-1}\right)^{-1}P\left(ya^{-1}\right) = ay^{-1}Pya^{-1}$. We know $y\sim a$ so $y^{-1}Py=a^{-1}Pa$ and therefore $ay^{-1}Pya^{-1} =aa^{-1}Paa^{-1} = P$ so $x \in \eqclass e$. We conclude then that $f_a$ is onto and therefore for any $a\in G$, $\card{\eqclass{a}} = \card{\eqclass e}$. It follows from this that the number of distinct $\eqclass a$ is $\frac{\card G}{\card{\eqclass e}}$ We know $\card G = p^nm$ and $\card{\eqclass{e}} =p^nk$ for some $k$, we then get the number of distinct equality classes to be $\frac mk$. Due to $m$ not being divisible by $p$ then $\frac mk$ must also not be divisible by $p$ as it is a divisor of $m$. Therefore we conclude that the number of distinct equivalence classes, also the number of distinct $x^{-1}Px$ can not be a multiple of $p$.

\subsubsection{Question 18}
Let $a \in N(N(P))$, with $P$, $p$-Sylow. It follows that $a^{-1}N(P)a\subset N(P)$. We know $P \subset N(P)$ so $a^{-1}Pa\subset a^{-1}N(P)a\subset N(P)$. Now we have $a^{-1}Pa$ as a $p$-Sylow subgroup of $N(P)$. $N(P)$ contains only one $p$-Sylow subgroup, $P$ (as we have already shown in a previous question) so $a^{-1}Pa = P$. Now we have that $a\in N(P)$ and therefore $N(N(P)) \subset N(P)$. We already had $N(P)\subset N(N(P))$ as this is true for any subgroup $H$ of $G$ that $H\subset N(H)$ and $N(P)$ is a subgroup of $G$. We now conclude $N(N(P)) = N(P)$.

%We already know that $N(P) \subset N(N(P))$ as for any subgroup $H$ of $G$ we have $H \subset N(H)$ and $N(P)$ is a group in $G$. Next consider $x \in N(N(P))$, this implies that $x^{-1}N(P)x = N(P)$. Now consider $y \in N(P)$, this implies that $y^{-1}Py = P$ and $x^{-1}yx \in N(P)$. We follow this out to get that $\left(x^{-1}yx\right)^{-1}Px^{-1}yx = P = x^{-1}y^{-1}xPx^{-1}yx$. We extrapolate that $xPx^{-1}=y^{-1}xPx^{-1}y$ so $y \in N\left(xPx^{-1}\right)$. This implies that $N(P)\subset N\left(xPx^{-1}\right)$. It follows that $y = xpx^{-1}$ for some $p\in P$ and therefore $x^{-1}yx = p$ so $x^{-1}yx \in P$. We now get $x^{-1}N(P)x\subset P$ and as $P\subset N(P)$ we then have $x^{-1}Px\subset P$. From this it follows that $x^{-1}Px = P$ as we saw in the section on normal subgroups. We now conclude that $x\in N(P)$ so $N(P) = N(N(P))$. Note that at no point did this make use of $P$ being and special subgroup of $G$ so this holds for all subgroups of $G$.

Obviously if $\card G = p^n$, then $G$ contains the trivial subgroup of order $p^n$, itself. Now assume that for some $m$ with $0 \le m \le n$ that there is a subgroup of $G$ with order $p^m$, from this and theorem 2.11.6, we get that there is a subgroup of this group (the one with order $p^m$) that has order $p^{m-1}$, so we get $G$ having a subgroup of order $p^m$ implies $G$ has a subgroup of order $p^{m-1}$. Now we finish by invoking induction and we have shown that for all $m$, $0\le m \le n$ that $G$ has a subgroup of order $p^m$.

\subsubsection{Question 25}
First a lemma from a previous problem that was not assigned.
\begin{lemma}\label{Q25}
	Suppose $a \in G$ such that $o(a) = p^m$, and $a^{-1}Pa = P$, with $P$ a $p$-Sylow subgroup of $G$ then $a\in P$.
\end{lemma}
\begin{proof}
	First we get that for all $k$, $a^-kPa^k = P$, and it follows that $Pa^k=a^{-k}P$. It follows from this that $(a)P=P(a)$, so let us show that this is a subgroup of $G$. Any element will have the form $a^kp$, with $p\in P$ so
	\begin{itemize}
		\item $a^{k_1}p_1a^{k_2}p_2 = a^{k_1+k_2}\left(a^{-k_2}p_1a^{k_2}\right)p_2 \in (a)P$.
		\item $\left(a^kp\right)^{-1}=p^{-1}a^{-m} = a^{-m}\left(a^mp^{-1}a^{-m}\right) \in (a)P$.
	\end{itemize}
	so we get $(a)P$ is a group. Now the order of $(a)P$ must be $\frac{\card{(a)}\card P}{\card{(a)\inter P}} = \frac{p^mp^n}{\card{(a)\inter P}}$. This must then be in the form $p^k$ for some $k$, so $k \le n$ as we have a $p$-Sylow group of order $p^n$. Now we then get that $\card{(a)\inter P} = p^m$ which is the order $(a)$ and thus $(a)\subset P$.
\end{proof}
Now let $P$ and $Q$ be $p$-Sylow subgroups of $G$ and $Q\not=P$. Consider $a\in P\inter N(Q)$ it follows that $a\in N(Q)$ so $a^{-1}Qa = Q$. By our lemma we have that $a \in Q$ and as $a \in P$ it's order must divide the order of $P$ so we get $a \in Q$. It follows then that $P\inter N(Q) \subset P\inter Q$ and as $P\not=Q$ then $P\inter Q \not=P$. Now $P\inter Q$ is a subgroup of $P$ and as $P\inter N(Q)$ is a subgroup of that we get $P\inter N(Q)$ is a subgroup of $P$ so its order must divide $p$ and not be $p^n$. Now we get $i_P(N(Q)\inter N) = p^k  > 1$, and as $i_G(N(H))$ is the number of double co-sets of $H$ in $G$ we get that the number of double co-sets of $Q$ in $P$ is in the form $p^k > 1$ so must be a multiple of $p$.

\subsubsection{Question 26}
Let $P$ be $p$-Sylow. For any $Q\not=P$ such that $Q$ is $p$-Sylow we get a multiple of $p$, $kp$ distinct double co-sets of $Q$, which in turn are all $p$-Sylow subgroups of $G$ and are not $P$. Therefore we get the number of distinct $p$-Sylow subgroups of $G$ must be 1 plus a multiple of $p$ as we have $P$ and a multiple of $p$ other $p$-Sylow groups.

\subsubsection{Question 28}
Suppose $H$ is a subgroup of $G$ with order $p^m$ and further assume that it is not contained in any $p$-Sylow subgroup of $G$. Now consider $Q$, a $p$-Sylow subgroup of $G$ and let $a \in H\inter N(Q)$ and we find that $a \in Q$ by our lemma $\ref{Q25}$ in my answers (part of question 25). Therefore it follows that $H\inter Q \supset H\inter N(Q)$. Now consider $i_H(H\inter N(Q)) = \frac{p^k}{p^m}\not=1$ and we know $k\not=p$ as that would imply that $H\subset Q$ and contradict the assumption that it is not contained in a $p$-Sylow group. Now we find that there is a multiple of $p$ double co-sets for any $p$-Sylow group, $Q$ and therefore a multiple of $p$, $p$-Sylow groups. This contradicts the fact that there is always $1$ plus a multiple of $p$, $p$-Sylow groups so $H$ must be contained in a $p$-Sylow group.

\section{Chapter 3}
\subsection{Section 1}
\subsubsection{Question 1}
\question{(a)} $(4, 5,2,1,3,6)$

\question{(b)} $(3,1,2,4,5)$

\question{(c)} $(1, 4, 3, 2, 5)$
